Simulation for generic Cormotif model

### 2017-09-25 analysis/Simulation_generic_Cormotif.Rmd
wflow_publish("Simulation_generic_Cormotif.Rmd")

```{r,cache=TRUE}
source('~/Git/cormotif/code/function.R')
K = 4
D = 4
G = 5000
sigma2 = c(100,100,100,100)
pi0 = c(0.2,0.2,0.2,0.4)
q0 = matrix(0,nrow=K,ncol=D)
q0[1,] = c(1,1,1,1)
q0[2,] = c(1,1,0,0)
q0[3,] = c(0,1,1,0)
q0[4,] = c(0,0,0,0)
X = matrix(0,nrow=G,ncol=D)
rows = rep(1:K,times=pi0*G)
A = q0[rows,]
set.seed(111)
for(g in 1:G){
  for(d in 1:D){
    if(A[g,d]==1){
      X[g,d] = rnorm(1,0,sqrt(1+sigma2[d]))
    } else{
      X[g,d] = rnorm(1,0,1)
    }
  }
}
betahat=X
sebetahat=matrix(1,nrow=G,ncol=D)
fit = generic.cormotif(betahat,sebetahat,K=1:5)
```

>>>>

```{r,cache=TRUE}
source('~/Git/cormotif/code/function.R')
K = 4
D = 4
G = 5000
sigma2 = c(100,100,100,100)
pi0 = c(0.2,0.2,0.2,0.4)
q0 = matrix(0,nrow=K,ncol=D)
q0[1,] = c(1,1,1,1)
q0[2,] = c(1,1,0,0)
q0[3,] = c(0,1,1,0)
q0[4,] = c(0,0,0,0)
X = matrix(0,nrow=G,ncol=D)
rows = rep(1:K,times=pi0*G)
A = q0[rows,]
set.seed(111)
for(g in 1:G){
  for(d in 1:D){
    if(A[g,d]==1){
      X[g,d] = rnorm(1,0,sqrt(1+sigma2[d]))
    } else{
      X[g,d] = rnorm(1,0,1)
    }
  }
}
betahat=X
sebetahat=matrix(1,nrow=G,ncol=D)
```

```{r,cache=TRUE}
fit = generic.cormotif(betahat,sebetahat,K=1:5)
```
